Pathogen Spillover - dissertation chapter

### 2018-10-10 pathogen-spillover-diss-ch.Rmd
Edit exported figure dimensions.

cowplot::plot_grid(
      inf.lfct.plot,
      inf.h2005.plot +
            xlab("Tree diversity (H')"),
      inf.hrs1422.plot,
      slc_vs_bay_plot +
            ggtitle(""),
      slc_vs_hrs25_plot +
            ggtitle(""),
      shannon.plot +
            ggtitle(""),
      hot.mod.plot +
            ggtitle(""),
      labels = "auto", label_x = .01
      )

>>>>

(sig.rel.fig <- cowplot::plot_grid(
      inf.lfct.plot,
      inf.h2005.plot +
            xlab("Tree diversity (H')"),
      inf.hrs1422.plot,
      slc_vs_bay_plot +
            ggtitle(""),
      slc_vs_hrs25_plot +
            ggtitle(""),
      hot.mod.plot +
            ggtitle(""),
      shannon.plot +
            ggtitle(""),
      labels = "auto", label_x = .01
      )
)
ggsave("figures/path-significant-relationships.png", plot = sig.rel.fig,
       width = 7, height = 7, units = "in")
